Cost- and Deadline-Constrained Provisioning for Scientific Workflow Ensembles in IaaS Clouds

### 2013-04-09 paper/paper.tex
Re-add granularity section

%\subsection{Task Granularity}
%\TODO{Should we remove this section?}
%
%In the last experiment we noted that, for Montage and CyberShake, the short
%runtimes of their tasks made the dynamic algorithms perform better relative to
%SPSS. In order to test this theory we adjusted the granularity of the tasks in
%several Montage and CyberShake ensembles to see how this would affect the
%relative performance of the algorithms. The granularity adjustment was
%achieved by multiplying the runtime of each task by a fixed scaling factor.

%Fig.~\ref{fig:stretching} shows the relative performance of the algorithms
%as the scaling factor is increased from 1 to 16. The figure only shows results
%for the CyberShake application with Pareto unsorted ensembles, but similar
%results were found for other ensemble types for both Montage and CyberShake.
%Each data point in the figure represents 500 simulations (5 ensembles with 10
%budgets and 10 deadlines). The best scores percent was calculated the same way
%as it was for Fig.~\ref{fig:distributions}.

%The figure shows that, as the scaling factor increases beyond 2, the relative
%performance of SPSS surpasses that of the dynamic algorithms. Similar results
%were found for other ensemble types for both applications. This result
%suggests that, in general, for fine-grained workflows the dynamic algorithms
%will produce better scores, and for coarse-grained workflows SPSS will produce
%better scores.

%\begin{figure}[tb]
 %   \centering
 %   \includegraphics[width=0.3\textwidth]{stretching_cybershake}
 %   \caption{Percentage of high scores achieved by each algorithm for Pareto 
 %   unsorted CyberShake ensembles when task runtime is scaled by a constant 
 %   factor. A scaling factor of $x$ means that the runtime of tasks in each 
 %   workflow was multiplied by $x$.}
%    \label{fig:stretching}
%\end{figure}

>>>>

\subsection{Task Granularity}

In the last experiment we noted that, for Montage and CyberShake, the short
runtimes of their tasks made the dynamic algorithms perform better relative to
SPSS. In order to test this theory we adjusted the granularity of the tasks in
several Montage and CyberShake ensembles to see how this would affect the
relative performance of the algorithms. The granularity adjustment was
achieved by multiplying the runtime of each task by a fixed scaling factor.

Fig.~\ref{fig:stretching} shows the relative performance of the algorithms
as the scaling factor is increased from 1 to 16. The figure only shows results
for the CyberShake application with Pareto unsorted ensembles, but similar
results were found for other ensemble types for both Montage and CyberShake.
Each data point in the figure represents 500 simulations (5 ensembles with 10
budgets and 10 deadlines). The best scores percent was calculated the same way
as it was for Fig.~\ref{fig:distributions}.

The figure shows that, as the scaling factor increases beyond 2, the relative
performance of SPSS surpasses that of the dynamic algorithms. Similar results
were found for other ensemble types for both applications. This result
suggests that, in general, for fine-grained workflows the dynamic algorithms
will produce better scores, and for coarse-grained workflows SPSS will produce
better scores.

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.3\textwidth]{stretching_cybershake}
    \caption{Percentage of high scores achieved by each algorithm for Pareto 
    unsorted CyberShake ensembles when task runtime is scaled by a constant 
    factor. A scaling factor of $x$ means that the runtime of tasks in each 
    workflow was multiplied by $x$.}
    \label{fig:stretching}
\end{figure}
